---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

[![Travis build status](https://travis-ci.org/zamorarr/ppcongress.svg?branch=master)](https://travis-ci.org/zamorarr/ppcongress)

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
# ppcongress

The goal of ppcongress is to provide an R interface to [ProPublica's Congress API](https://projects.propublica.org/api-docs/congress-api/). The following endpoints have been mapped:

- [members](https://projects.propublica.org/api-docs/congress-api/members/)

The following endpoints are on the roadmap:

- [bills](https://projects.propublica.org/api-docs/congress-api/bills/)
- [votes](https://projects.propublica.org/api-docs/congress-api/votes/)
- [statements](https://projects.propublica.org/api-docs/congress-api/statements/)
- [committees](https://projects.propublica.org/api-docs/congress-api/committees/)

Please file an [issue](https://github.com/zamorarr/ppcongress/issues) if there are other endpoints you want added.

## Example

```{r load-pkg}
library(ppcongress)
```

You can get a list of all the members of the 116th congress in the house with the `members()` function:

```{r house-116, cache=TRUE}
json <- members("house", 116)
print(json)
```

The function `as_tibble()` will convert this list object to a data frame:

```{r as_tibble}
df <- as_tibble(json)
str(df)
```

## Installation

You can install the development version of ppcongress from [GitHub](https://github.com/zamorarr/ppcongress) with:

```r
remotes::install_github("zamorarr/ppcongress")
```

You also need to sign up to get an API Key from [ProPublica's Data Store](https://www.propublica.org/datastore/api/propublica-congress-api). Put this key in your *.Renviron* file by opening it:

```r
usethis::edit_r_environ()
```

Then adding the following line, replacing XXX with your own key.

```sh
PROPUBLICA_API_KEY=XXX
```
